---
title: "Practical Machine Learning Project"
output: html_document
---

### Introduction
The project based on a large set of data about personal activity. The model is developed to classify whether a barbel lifts is correct or not, based on the data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants.

##### Data Source
The training data for this project are available here: 

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here: 

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

#### Library and data

Following packages and libraries were used in this project.

```{r,results='hide',warning=FALSE,message=FALSE}
library(Hmisc)
library(caret)
library(randomForest)
library(knitr)
set.seed(1024)
```

#### Data read-in and preprocessing

Setting workindg directory (If you want to run this R markdown file, please modify this line)
```{r}
setwd("H:/Dropbox/CS/DataScience/PracMachine/Project")
```

Read-in data
```{r}
data_train <- read.csv("pml-training.csv", na.strings= c("NA",""," ","#DIV/0!"))
data_test <- read.csv("pml-testing.csv", na.strings= c("NA",""," ","#DIV/0!"))
```

Pre-processing data, removing rows with NA.
```{r}
data_train <- data_train[,colSums(is.na(data_train))==0]
data_test <- data_test[,colSums(is.na(data_test))==0]
data_train <- data_train[,-c(1:7)]
data_test <- data_test[,-c(1:7)]
```

#### Model building

Split __data_train__ (training data) into training and cross validation.
```{r}
inTrain <- createDataPartition(y = data_train$classe,p=0.7,list=FALSE)
training <- data_train[inTrain,]
crossValidation <- data_train[-inTrain,]
dim(training);dim(crossValidation)
```

Build the model
```{r}
model <- randomForest(classe ~., data = training)
```

Because of long run time in making the model, the last part is cached. Here is the built model.
```{r,results='markup'}
model
```
The model looks conviencible with __OOB estimate of error rate being 0.47%__

Cross Validation
```{r}
CroVal <- predict(model, crossValidation)
confusionMatrix(crossValidation$classe,CroVal)
```
Here from the confusion matrix, we can see that we did a good job on cross validation with __99.52% accuracy__.

#### Prediction
Then we use the model we just built to run with testing data set. This is a general prediction, not for Coursera Submission. The next part will detail the submission part. 
```{r}
## Remove some part of test data for submission
## The last row is problem_id, not a predictor
data_test_n <- data_test[1:length(data_test)-1]
pred_result <- predict(model, data_test_n)
pred_result
```

#### Cousera Submission
```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(pred_result)
```
